Higher-Order unification for free!

### 2024-07-01 paper/main.tex
rework last paragraph abstract

  In this paper we propose a more well-behaved encoding called \Ho,
  and show how to translate unification problems from \Fo{}
  to corresponding ones in \Ho.
  Consequently, we derive \Uo{}, the higher-order unification procedure of \Fo{}
    that honours $\eta\beta$-equivalence (for Coq functions), addresses
  problems within the pattern fragment, and allows
  for the use of heuristics to deal with problems outside the
  pattern fragment. Moreover, as \Uo{} delegates most of the work to \Ue,
  it can be used to efficiently simulate a logic program in \Fo{} by
  taking advantage of
  unification-related optimizations of the meta language, such as clause indexing.

>>>>

  In this paper we propose to translate \Fo{} unification problems
  into an alternative encoding called \Ho, from which we derive \Uo,
  the higher-order unification procedure of \Fo{}. \Uo
  honours $\eta\beta$-equivalence for terms
  within the pattern fragment, and allows the use for 
  heuristics when unification is performed with terms outside the pattern fragment.
  Moreover, as \Uo{} delegates most of the work to \Ue,
  it can be used to efficiently simulate a logic program in \Fo{} by
  taking advantage of
  unification-related optimizations of the meta language, such as clause indexing.
